Hybrid platforms and bargaining power

### 2024-06-10 src/paper/application.tex
Move extensions to appendix
Fix some references

The most important, and perhaps surprising, results of this theorem is that the platform's product variety has no effect on consumer welfare in the hybrid regime.
This is due to the fact that the optimal entry fee, which is independent of $N_P$, pins down the aggregate.
As shown in \cref{fig:fig:fringe_entry_eq}, an increase in the platform's product variety will simply replace fringe firms in a constant ratio, such that the aggregate remains constant (\cref{fig:welfare_aggregate}).
This, in turn, implies that consumer surplus is also unaffected by the platform's product variety in the hybrid regime, as demonstrated in \cref{fig:welfare_consumer}.

>>>>

The most important, and perhaps surprising, results of this theorem is that the platform's product variety has no effect on consumer welfare in the hybrid regime.
This is due to the fact that the optimal entry fee, which is independent of $N_P$, pins down the aggregate.
As shown in \cref{fig:fringe_entry_eq}, an increase in the platform's product variety will simply replace fringe firms in a constant ratio, such that the aggregate remains constant (\cref{fig:welfare_aggregate}).
This, in turn, implies that consumer surplus is also unaffected by the platform's product variety in the hybrid regime, as demonstrated in \cref{fig:welfare_consumer_surplus}.
